### 2017-11-20 final-paper/paper.la_.tex
feat(paper): added base LaTeX file and readme with tips

% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file.

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Byteboy : A Byteman Companion Application}

\author{
{\rm Alex P. T. Macdonald}\\
apmacdon@sfu.ca\\
Simon Fraser University
\and
{\rm Ian Pun}\\
Simon Fraser University
} % end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}

\subsection*{Abstract}
Your Abstract Text Goes Here.  Just a few facts.
Whet our appetites.

\section{Introduction}

A paragraph of text goes here.  Lots of text.  Plenty of interesting
text. \\

More fascinating text. Wow this paper is so interesting. It's incredible.\\

\section{Background}

Some embedded literal typset code might 
look like the following :

{\tt \small
\begin{verbatim}
int wrap_fact(ClientData clientData,
              Tcl_Interp *interp,
              int argc, char *argv[]) {
    int result;
    int arg0;
    if (argc != 2) {
        interp->result = "wrong # args";
        return TCL_ERROR;
    }
    arg0 = atoi(argv[1]);
    result = fact(arg0);
    sprintf(interp->result,"%d",result);
    return TCL_OK;
}
\end{verbatim}
}

% This will be useful for citations, don't remove just yet.
Now we're going to cite somebody.  Watch for the cite tag.
Here it comes~\cite{Chaum1981,Diffie1976}.  The tilde character (\~{})
in the source means a non-breaking space.  This way, your reference will
always be attached to the word that preceded it, instead of going to the
next line.

\section{Motivation}
\subsection{A Poem}

Roses are Red. \\
Violets are Blue. \\
Omae wa mou shindeiru \\

% HELPFUL STUFF ON HOW TO EMBED IMAGES
% you can also use the wonderful epsfig package...
% \begin{figure}[t]
% \begin{center}
% \begin{picture}(300,150)(0,200)
% \put(-15,-30){\special{psfile = fig1.ps hscale = 50 vscale = 50}}
% \end{picture}\\
% \end{center}
% \caption{Wonderful Flowchart}
% \end{figure}

% This text came after the figure, so we'll casually refer to Figure 1
% as we go on our merry way.

\subsection{Here's some neat stuff I'm not going to remove yet because it'll be pretty useful for our motivating example I think when showing how to run the code}

Sometimes you want to really call attention to a piece of text.  You
can center it in the column like this:
\begin{center}
{\tt \_1008e614\_Vector\_p}
\end{center}
and people will really notice it.\\

\noindent
The noindent at the start of this paragraph makes it clear that it's
a continuation of the preceding text, not a new para in its own right.

Now this is an ingenious way to get a forced space.
{\tt Real~$*$} and {\tt double~$*$} are equivalent.

Now here is another way to call attention to a line of code, but instead
of centering it, we noindent and bold it.\\

\noindent
{\bf \tt size\_t : fread ptr size nobj stream } \\

And here we have made an indented para like a definition tag (dt)
in HTML.  You don't need a surrounding list macro pair.
\begin{itemize}
\item[]  {\tt fread} reads from {\tt stream} into the array {\tt ptr} at
most {\tt nobj} objects of size {\tt size}.   {\tt fread} returns
the number of objects read. 
\end{itemize}
This concludes the definitions tag.

\section{Approach}

This is where our approach will go. \\

\section{Evaluation \& Observations}

This is where our evaluation \& observations will go. \\

\section{Related Work}

This is where related work goes. \\

\section{Conclusion \& Future Work}

This is where the conclusion goes. \\

\section{Acknowledgments}

Good night Springton, there will be no encores. \\

\end{document}

### 2017-11-21 main.py
small changes to main.py to be more modular

@@ -7,19 +7,11 @@
 import os
 import sys
 
+from analysis import run_analysis
+
 def main(java_file):
     
-    # Runs the profiler on the provided java class
-    os.system("java -agentlib:hprof=cpu=times " + java_file)
-    
-    # Reads in the results, dumps some of it to the console
-    results = open("./java.hprof.txt", "r").read()
-    print(results[results.find("CPU TIME (ms)"):])
-
-    # print command line arguments
-    print("testing")
-    for arg in sys.argv[1:]:
-        print(arg)
+    run_analysis(java_file)
 
 if __name__ == "__main__":
     try:

### 2017-11-21 analysis.py
analysis.py skeleton code thats currently able to parse hprof rankings

@@ -1,0 +1,34 @@
+#!/usr/bin/python3
+
+# analysis.py
+# CMPT 479 - Final Project
+# Contributors: itpun, aptmac
+
+import os
+import sys
+import subprocess
+
+def run_analysis(java_file_path):
+    """returns a .txt file with analysis details for interactive"""
+    # Runs the profiler on the provided java class
+    # ranked methods by time (5 to 10)
+    # Need its method name, CPU usage,  arguments, argmuent types, whats calling it (stack trace),
+    # TODO: figure out argument/agrument types
+    if os.path.exists(java_file_path):        
+        # check to see if it is a relative path or if there is something there already
+        fullpath =  os.path.realpath(java_file_path)  
+        print "Analyzing..."
+        flags = " -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath)
+        # look into subprocesses for refactoring!
+        os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath))
+        # Reads in the results, dumps some of it to the console
+        results = open("./java.hprof.txt", "r")
+        for line in results:
+            if "rank " in line:
+                for entry in results:
+                    entrysplit =entry.split()
+                    print "test"
+                    print entrysplit
+
+    else:
+        print ("Java file does not exist.")

### 2017-11-21 analysis.py
additional analysis work. Getting stace trace methods in progress

@@ -9,6 +9,16 @@ import sys
 import subprocess
 
 def run_analysis(java_file_path):
+    #HPROF ranking indexes
+
+    TOTAL_RANKINGS = 5
+    RANK   = 0
+    SELF   = 1
+    ACCUM  = 2
+    COUNT  = 3
+    TRACE  = 4
+    METHOD = 5
+
     """returns a .txt file with analysis details for interactive"""
     # Runs the profiler on the provided java class
     # ranked methods by time (5 to 10)
@@ -23,12 +33,32 @@ def run_analysis(java_file_path):
         os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath))
         # Reads in the results, dumps some of it to the console
         results = open("./java.hprof.txt", "r")
-        for line in results:
-            if "rank " in line:
-                for entry in results:
-                    entrysplit =entry.split()
-                    print "test"
-                    print entrysplit
+        rankings = list()
+        trace_search_list = list()
 
+        for line in results:                
+            if "rank " in line:
+                #for entry in results:
+                for index, entry in enumerate(results):
+                    if (index < TOTAL_RANKINGS):
+                        temp_list = entry.split()
+                        trace_search_list.append("TRACE " + temp_list[TRACE] + ":") 
+                        del temp_list[SELF]
+                        rankings.append(temp_list)
+                    else: break
+        search_index = 0 
+        results = open("./java.hprof.txt", "r")
+        for line in results:
+            print "searching for " + trace_search_list[search_index]
+            if trace_search_list[search_index] in line:
+                print "found at " + trace_search_list[search_index]
+                for method in results:
+                    if ("TRACE " not in method):
+                        rankings[search_index].append(method)
+                    else:
+                        search_index += 1
+                        print "increase search index"
+                        break
+        #print rankings
     else:
         print ("Java file does not exist.")

### 2017-12-04 tests/A.java
feat(tests): add a few programs that can be potentially used as test cases

@@ -1,0 +1,48 @@
+/**
+ * A.java
+ * Author: RedEyes
+ * Borrowed from Stack Overflow: https://stackoverflow.com/questions/30968231/whats-wrong-with-my-code
+ */
+
+import java.awt.*;
+import javax.swing.*;
+import java.awt.event.*;
+
+class A implements ActionListener {
+
+    JFrame f;
+    JButton b;
+    JPanel p;
+    JLabel l;
+    JTextField t;
+
+    A(String s) {
+        JFrame f=new JFrame(s);
+        f.setVisible(true);
+        f.setSize(400,400);
+        JButton b= new JButton("OK");
+        JTextField t=new JTextField();
+        JPanel p=new JPanel(); 
+        f.add(p);
+        p.setBounds(0,0,300,300);
+        p.add(b);
+        b.setBounds(30,40,80,80);
+        p.add(t);
+        t.setBounds(100,200,80,80);
+        b.addActionListener(this);
+        t.addActionListener(this);
+        f.setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
+    }
+
+    public void actionPerformed(ActionEvent e) {
+        if(e.getSource() == b) {    
+            t.setText("Hey There");
+        }
+        System.out.println("I m done!!");
+    }
+
+    public static void main(String[] args) {
+         System.out.println("Hey there");  
+         new A("First App");  
+    }
+}

### 2017-12-04 analysis.py
additional work on anaylsis, able to parse away metacharacters from method string. Currently able to spill full relevant stack traces

@@ -7,6 +7,7 @@
 import os
 import sys
 import subprocess
+import re
 
 def run_analysis(java_file_path):
     #HPROF ranking indexes
@@ -46,19 +47,31 @@ def run_analysis(java_file_path):
                         del temp_list[SELF]
                         rankings.append(temp_list)
                     else: break
+
+        # for line in results:
+        #     if trace_search_list[search_index] in line:
+        #         print "found at " + trace_search_list[search_index]
+        #         for method in results:
+        #             if ("TRACE " not in method):
+        #                 rankings[search_index].append(method)
+        #             else:
+        #                 search_index += 1
+        #      #           print "increase search index"
+        #                 break
+        # #print rankings
         search_index = 0 
-        results = open("./java.hprof.txt", "r")
-        for line in results:
-            print "searching for " + trace_search_list[search_index]
-            if trace_search_list[search_index] in line:
-                print "found at " + trace_search_list[search_index]
-                for method in results:
-                    if ("TRACE " not in method):
-                        rankings[search_index].append(method)
-                    else:
-                        search_index += 1
-                        print "increase search index"
-                        break
-        #print rankings
+        for search_query in trace_search_list:
+            results = open("./java.hprof.txt", "r")
+            for line in results:
+                if search_query in line:
+                    for method in results:
+                        if ("TRACE " not in method):
+                            method = re.sub(r'\t', '', method)
+                            method = re.sub(r'\n', '', method)
+                            rankings[search_index].append(method)
+                        else:
+                            search_index += 1
+                            break
+        print rankings
     else:
         print ("Java file does not exist.")

### 2017-12-04 final-paper/paper.la_.tex
feat(paper): added references to the latex file

@@
 
+\begin{thebibliography}{99}
+
+\bibitem{bytemanwebsite} 
+Byteman: Simplify Java tracing, monitoring and testing with Byteman,
+\\\texttt{http://byteman.jboss.org/}
+
+\bibitem{bytemanguide}
+Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
+\\\texttt{http://downloads.jboss.org/byteman/3.0.10/ProgrammersGuide.html}
+
+\bibitem{yo}
+Yo Code - Extension Generator
+\\\texttt{https://code.visualstudio.com/docs/extensions/yocode}
+
+\bibitem{textmate}
+Textmate: Language Grammars
+\\\texttt{https://manual.macromates.com/en/language\_grammars}
+
+\bibitem{bytemanvideo}
+Dinn, Andrew. \\\textit{Monitoring Application-Specific Behavior Using Thermostat and Byteman}
+YouTube. 2016. URL: \\\texttt{https://www.youtube.com/watch?v=teL7qnulUTM}
+
+\end{thebibliography}
+
 \end{document}

### 2017-12-04 analysis.py
added threshold to ranking check. Currently only reports methods using more than 20% CPU power

@@ -11,7 +11,6 @@ import re
 
 def run_analysis(java_file_path):
     #HPROF ranking indexes
-
     TOTAL_RANKINGS = 5
     RANK   = 0
     SELF   = 1
@@ -19,6 +18,8 @@ def run_analysis(java_file_path):
     COUNT  = 3
     TRACE  = 4
     METHOD = 5
+
+    THRESHOLD = 20
 
     """returns a .txt file with analysis details for interactive"""
     # Runs the profiler on the provided java class
@@ -29,8 +30,6 @@ def run_analysis(java_file_path):
         # check to see if it is a relative path or if there is something there already
         fullpath =  os.path.realpath(java_file_path)  
         print "Analyzing..."
-        flags = " -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath)
-        # look into subprocesses for refactoring!
         os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath))
         # Reads in the results, dumps some of it to the console
         results = open("./java.hprof.txt", "r")
@@ -43,22 +42,14 @@ def run_analysis(java_file_path):
                 for index, entry in enumerate(results):
                     if (index < TOTAL_RANKINGS):
                         temp_list = entry.split()
-                        trace_search_list.append("TRACE " + temp_list[TRACE] + ":") 
-                        del temp_list[SELF]
-                        rankings.append(temp_list)
+                        # check to see if the process is passing CPU usage threshold
+                        if (float(temp_list[SELF].strip("%")) >= THRESHOLD):
+                            trace_search_list.append("TRACE " + temp_list[TRACE] + ":") 
+                            # ignore method name as it will appear in stack trace and accum as they are not useful for diagnostic anymore
+                            del temp_list[METHOD]
+                            del temp_list[ACCUM]
+                            rankings.append(temp_list)
                     else: break
-
-        # for line in results:
-        #     if trace_search_list[search_index] in line:
-        #         print "found at " + trace_search_list[search_index]
-        #         for method in results:
-        #             if ("TRACE " not in method):
-        #                 rankings[search_index].append(method)
-        #             else:
-        #                 search_index += 1
-        #      #           print "increase search index"
-        #                 break
-        # #print rankings
         search_index = 0 
         for search_query in trace_search_list:
             results = open("./java.hprof.txt", "r")
[…]

### 2017-12-05 final-paper/paper.la_.tex
feat(paper): added bulk of the paper, currently need to finish approach, results, and related work

@@
 \usepackage{usenix,epsfig,endnotes}
+
 \begin{document}
@@
 {\rm Alex P. T. Macdonald}\\
-apmacdon@sfu.ca\\
+apmacdon[at]sfu.ca\\
 Simon Fraser University
@@
 
-% Use the following at camera-ready time to suppress page numbers.
-% Comment it out when you first submit the paper for review.
-\thispagestyle{empty}
+\subsection*{ABSTRACT}
+As computer programs grow larger and more complex, the likelihood of catastrophic issues may increase over time.
+Although many bugs can be discovered by using modern testing frameworks, some bugs may go unrecognized and appear in production builds.
 
-\subsection*{Abstract}
-Your Abstract Text Goes Here.  Just a few facts.
-Whet our appetites.
+Byteman is a powerful open-source tracing and debugging tool for Java, that injects Java code into application methods without the need of recompilation, repackaging, or even redeploying the application.
+However, the Byteman scripting language syntax is not currently supported by IDEs, and learning how to write Byteman rules is a completely manual and potentially tedious process.
+Currently, learning Byteman requires the user to either read the User's Manual, or search for tutorial blog posts that can be adapted to fit their needs.
 
-\section{Introduction}
+This paper presents Byteboy, a companion application suite for Byteman which includes a semi-automatic rule builder, a VS Code language extension, and a basic fuzz test generator for the Byteman scripting language.
 
-A paragraph of text goes here.  Lots of text.  Plenty of interesting
-text. \\
+\section{INTRODUCTION}
 
-More fascinating text. Wow this paper is so interesting. It's incredible.\\
+Writing bug free software is often easier said than done.
+Modern compilers and testing frameworks will often help developers minimize the number of bugs that make it into production environments, but there is no guarantee that the end result will be completely error free.
+For example, a Java program with poor exception handling coverage may pass a syntax check, but will crash if an unexpected exception type is thrown in response to an input.
+As a result, there is a need for tools that can diagnose and repair software bugs in runtime environments, and can interact with the program code in order to either create a temporary fix, or reveal the root cause of the error such that a proper fix can be developed.
 
-\section{Background}
+An example of a tool that is capable of diagnosing and repairing errors in Java programs is Byteman\cite{bytemanwebsite}.
+Byteman is a bytecode injection tool, that allows the user to write code using the Byteman scripting language, which will be injected into a running application.
+Currently, there is no IDE language support for the Byteman scripting language, and the best methods of learing how to write rules includes reading the Programmer's Guide \cite{bytemanguide}, reading various tutorial blog posts\cite{bytemanblog}, or by watching a Byteman tutorial YouTube video\cite{bytemanvideo}.
+As a result, when looking at Byteman from the perspective of a first time user it may present a large learning curve, especially to a developer that is accustomed to the modern luxuries of language learning that include code snippets, hints, generators\cite{yoman}, and guided learning.
 
-Some embedded literal typset code might 
-look like the following :
+In this paper, we propose Byteboy, a companion application for Byteman.
+Byteboy provides functionality for manual and semi-automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension.
+Byteboy was designed to improve the Byteman user experience from the point of rule inception, through to actually implementing and shipping the proposed bug-fixing rule file.
+
+\section{BACKGROUND}
+
+\subsection{Byteman}
+
+Byteman is a tool for monitoring, debugging, and testing Java code\cite{bytemanwebsite}.
+It is a Java Virtual Machine Tool Interface (JVMTI) agent, which allows it to be installed via the command line to retrieve and interact with data from the Java Virtual Machine (JVM).
+Byteman modifies the bytecode of an application at runtime, and can inject into any Java methods (including the JDK runtime and libraries), and can even interact with private methods\cite{bytemanwebsite}.
+Unlike many other bytecode transformers, Byteman operates at the level of Java (not bytecode), so you provide Byteman with rules with specify the Java code you want to be executed, and Byteman works out how to rewrite the bytecode such that it behaves as if it were native to the source code\cite{bytemanwebsite}.
+
+\subsection{Byteman Rule Syntax}
+
+\noindent
+The syntax of a Byteman rule is as follows:
 
@@
 \begin{verbatim}
-int wrap_fact(ClientData clientData,
-              Tcl_Interp *interp,
-              int argc, char *argv[]) {
-    int result;
-    int arg0;
-    if (argc != 2) {
-        interp->result = "wrong # args";
-        return TCL_ERROR;
+RULE <unique-name>
+CLASS <classname>
+METHOD <method-name>
+AT <entry/exit>
+IF <condition>
+DO <action>
+ENDRULE
+\end{verbatim}
 }
-    arg0 = atoi(argv[1]);
-    result = fact(arg0);
-    sprintf(interp->result,"%d",result);
-    return TCL_OK;
+
+{\tt RULE} specifies the name of the rule, which will be used when unloading the rule, and should be unique for best practices.
+
+{\tt CLASS} specifies the class the rule wants to target.
+
+{\tt METHOD} specifies the target method within the selected class.
+
+{\tt AT} specifies the timing of which the rule logic should take place relative to the method.
+For example, {\tt AT ENTRY} causes the rule logic to execute when the target method is entered, and {\tt AT EXIT} can be used to execute code when the method has completed execution.
+
+{\tt IF} specifies a condition in which the rule logic will execute. This can be based on variable input, or conditions of interest, or could be left as {\tt TRUE} to always execute.
+
+{\tt DO} specifies the logic of the rule, in which actions will be executed.
+This is where the rule can bind to existing variables, create new variables (such as counters), or use traceln statements to print information to the console.
+
+{\tt ENDRULE} specifies the end of the rule content.
+A single Byteman script may contain many rules, so ensuring separation using the {\tt RULE} and {\tt ENDRULE} are important for passing syntax checks, but also for ensuring that individual rules can be unloaded at will without having to remove all of the rules.
+
+\subsection{Using Byteman}
+
+Byteman can be used on an application that is currently executing, or at start time.
+Byteman is a JVMTI agent, which allows it to be supplied to the {\tt javaagent} argument when running a Java application.
+
+If {\tt BYTEMAN\_HOME} is an environment variable that points to the current installed or downloaded version of Byteman, a script ({\tt rule.btm} in this case) can be loaded along side running the Java program {\tt HelloWorld} with the following command:
+
+\begin{center}
+\noindent
+{\tt java -javaagent=\$BYTEMAN\_HOME
+/lib/byteman.jar=script:rule.btm HelloWorld}
+\end{center}
+
+\noindent
+Please see the Byteman Programmer's Guide\cite{bytemanguide} for advanced syntax, use cases, and examples.
+
+\section{MOTIVATION}
+
+This section presents an example to illustrate how Byteman can be used to trace and debug bugs in Java programs.
+
+\subsection{Example Application}
+
+Consider the following Java program:
+{\tt \small
+\begin{verbatim}
+public class InfLoop {
+
+    private void doWork(int i) {
+        while(i == 0) {
+            work();
+        }
+    }
+
+    private static void work() {}
+
+    public static void main(String[] args) { 
+        InfLoop inf  = new InfLoop();
+        inf.doWork(0);
+    }
 }
@@
 
-% This will be useful for citations, don't remove just yet.
-Now we're going to cite somebody.  Watch for the cite tag.
-Here it comes~\cite{Chaum1981,Diffie1976}.  The tilde character (\~{})
-in the source means a non-breaking space.  This way, your reference will
-always be attached to the word that preceded it, instead of going to the
-next line.
+The above Java application contains a bug which will cause it to become stuck in an infinite loop.
+The main method instantiates a new InfLoop object, and decides to put the object to work.
+The InfLoop object has it's {\tt doWork()} method invoked and is passed the number zero, which allows entry into the while loop and causes {\tt work()} to be called.
+However, the developer of this program forgot to write an exit condition for the loop, and now the program will loop infinitely.
+While this program is simplistic for the sake of being an example, the behaviour of this object is not completely unbelievable; it would be completely understandable to have an object that enters a loop after calling a function.
 
-\section{Motivation}
-\subsection{A Poem}
+Compiling and running the above program will not throw any errors, and upon executing this program in the terminal, the user will be greeted with a blinking prompt while the program is stuck in execution.
+With no definitive indication of if or where an error is occurring, this is a good time to construct some Byteman rules.
 
-Roses are Red. \\
-Violets are Blue. \\
-Omae wa mou shindeiru \\
+\subsection{Tracing the Error}
 
-% HELPFUL STUFF ON HOW TO EMBED IMAGES
-% you can also use the wonderful epsfig package...
-% \begin{figure}[t]
-% \begin{center}
-% \begin{picture}(300,150)(0,200)
-% \put(-15,-30){\special{psfile = fig1.ps hscale = 50 vscale = 50}}
-% \end{picture}\\
-% \end{center}
-% \caption{Wonderful Flowchart}
-% \end{figure}
+The first step in debugging the above application will be to trace the error, and try to gather some information about the current program behaviour.
+Based on looking at the source code, a good point to start tracing may be the entry point of the {\tt work()} method, to see if the application is actually doing any work.
+In order to confirm or deny the activity of {\tt work()}, the following Byteman rule will be constructed:
 
-% This text came after the figure, so we'll casually refer to Figure 1
-% as we go on our merry way.
+{\tt \small
+\begin{verbatim}
+RULE Traceln when starting work
+CLASS InfLoop
+METHOD work
+AT ENTRY
+IF TRUE
+DO traceln("- We're starting work.");
+ENDRULE
+\end{verbatim}
+}
 
-\subsection{Here's some neat stuff I'm not going to remove yet because it'll be pretty useful for our motivating example I think when showing how to run the code}
+The above rule targets the entry point of the {\tt work()} method, and when called, will output a string to the console.
 
-Sometimes you want to really call attention to a piece of text.  You
-can center it in the column like this:
+After loading this Byteman rule into the running application, the console will be flooded with strings indicating the constant and relentless calling of the {\tt work()} method.
+At this point, it can be deduced that the program may be stuck in execution, and it may be a good time to consider a Byteman script that can relieve the application.
+
+\subsection{Debugging the Error}
+
+Now that the error has been traced and verified, a Byteman rule may be able to be constructed with the purpose of exiting the loop.
+Going back to the source code, it is evident that the reason {\tt work()} is being called so frequently is because it is being called from within a loop that will only exit if the variable i is changed such that it no longer equals zero.
+The variable i is an argument that is passed to {\tt doWork()} from the main method, and can be altered by the following Byteman rule:
+
+{\tt \small
+\begin{verbatim}
+RULE Exit The Loop 
+CLASS InfLoop
+METHOD doWork
+AT ENTRY
+IF TRUE
+DO
+$1 = 1;
+ENDRULE
+\end{verbatim}
+}
+
+The above rule targets the entry point of the {\tt doWork()} method, and uses the \$1 to bind to the first argument in the function declaration (which is i in this case), and re-assigns the value to 1.
+
+As a result, when running this program with the above rule injected, the program will not enter the infinite loop, and will allow the program to terminate.
+
+\subsection{Introducing Byteboy}
+
+As illustrated using the above Java program and Byteman rules, writing these rules requires knowledge of the target application and access to it's source code in order to design rules that accomplish a specific task.
+The above example involved a short Java program with a glaring and obvious bug, but what happens if a developer encounters an error in their application that spans thousands of lines of code, and maybe aren't intimately familiar with all aspects of the code base?
+Furthermore, modern IDEs have no support for the Byteman scripting language, which causes developers to write their scripts without the modern luxuries that language extensions offer.
+Finally, at the moment, the quickest way of learning to write Byteman rules would be from reading one of the many helpful blog posts\cite{bytemanblog} or YouTube videos\cite{bytemanvideo} that target beginner and first time users, but no tool currently exists that can help guide a user through the creation of their first scripts.
+
+Here, we wish to present Byteboy - a companion application for Byteman.
+Byteboy was designed to enhance the Byteman user experience by aiding the development of rules starting from the point of inception, through to the result of creating in a production-quality script.
+
+The primary functionality of Byteboy is it's rule generator, which can be used in a manual or semi-automatic capacity.
+The manual rule generation using Byteboy is reminiscent of the Yeoman Generator\cite{yoman}, in which the program will guide new and first-time users through the process of writing rules.
+The semi-automatic rule generation actually performs an execution of the target program, and collects and aggregates information about the application performance and code structure to generate a set of plausible rules.
+
+Another feature of Byteboy is it's fuzz test generator, in which it performs the same analysis of the semi-automatic rule generation, but instead of suggesting rules that could be used to trace or debug the code, it generates rules with the aim of producing unexpected behaviour in the source program.
+
+Lastly, Byteboy ships with a language extension for Visual Studio Code which provides support for the Byteman scripting language.
+
+\section{APPROACH}
+
+This section describes our approach for Byteboy.
+Here, we will primarily discuss the approach to the semi-automatic rule generator because it shares the same approach with the fuzz test generator, and the manual rule generator is just a simplified version of this approach.
+The approach is comprised of three phases to generate Byteman rules: Instrumentation, Analysis, and Synthesis.
+
+\subsection{Instrumentation}
+
+This is where we discuss hprof.
+
+\subsection{Analysis}
+
+This is where we discuss the Python application and why we used Python.
+
+\subsection{Synthesis}
+
+This is where we discuss how the rules get mashed together.
+
+\subsection{VS Code Language Extension}
+
+A feature that many developers take for granted is the language support extension for their favourite IDE.
+Popular IDEs such as Eclipse and Visual Studio Code offer support for various language extensions, and there are currently extensions available for the majority of modern languages.
+Despite this, Byteman currently has no publicly available language extension.
+
+In an attempt to remedy this situation, Byteboy ships with a Visual Studio Code language extension, that offers support for the Byteman scripting language and a basic rule generation snippet.
+The extension was initialized using the Yo Code generator\cite{yocode}, and uses the TextMate language grammar format\cite{textmate} to provide functionality to the IDE.
+Our TextMate grammar file is based on the Byteman syntax as described in the Byteman Programmer's Guide\cite{bytemanguide}, and includes coverage for the majority of the keywords and behaviours.
+
+The language extension is not yet currently available through the Extensions Marketplace, but future work efforts will be put forward towards a public release.
+Currently, the only method of installation would be to grab the {\tt byteman-language-extension} folder from the Byteboy repository, and copying it into the extensions folder located in the VS Code user settings folder.
+On Linux, this can be accomplished using the following command:
 \begin{center}
-{\tt \_1008e614\_Vector\_p}
+{\tt cp -r byteman-language-extension \textasciitilde/.vscode/extensions}
 \end{center}
-and people will really notice it.\\
+More instructions and details of usage can be found on the language-extension page of the Byteboy repository\cite{bytemanextension}.
 
-\noindent
-The noindent at the start of this paragraph makes it clear that it's
-a continuation of the preceding text, not a new para in its own right.
+\section{EVALUATION \& OBSERVATIONS}
 
-Now this is an ingenious way to get a forced space.
-{\tt Real~$*$} and {\tt double~$*$} are equivalent.
+We evaluate Byteboy using the previously described {\tt InfLoop} program, and four "real world" examples.
+We will also discuss the results of using Byteboy on the test cases, and the observations that were made as a result.
+Lastly, we will discuss the current shortcomings and limitations of Byteboy, and how they can potentially be overcome.
 
-Now here is another way to call attention to a line of code, but instead
-of centering it, we noindent and bold it.\\
+\subsection{Test Cases}
 
-\noindent
-{\bf \tt size\_t : fread ptr size nobj stream } \\
+The test cases for Byteboy include 4 buggy programs, including the {\tt InfLoop} example that has already been introduced.
+The other four programs are "real world" buggy programs, and we will describe the emphasis of the quotation marks here.
+Frankly, finding bugs in software that are easily and consistently reproducible is a lot harder than it sounds.
+Many popular applications will likely have had their obvious bugs patched already (assuming they made it through the review process in the first place), and many bugs that do exist may be difficult to reproduce or observe due to concurrency.
+Initially, we had attempted to use the GitHub search filters to find repositories containing Java applications with bugs that may be easily reproducible.
+However, we were instead met with a massive list of potential bugs (which is assuring), but the vast majority of them had poor documentation regarding how to reproduce the errors, let alone how to run the program itself (that's not so assuring).
 
-And here we have made an indented para like a definition tag (dt)
-in HTML.  You don't need a surrounding list macro pair.
-\begin{itemize}
-\item[]  {\tt fread} reads from {\tt stream} into the array {\tt ptr} at
-most {\tt nobj} objects of size {\tt size}.   {\tt fread} returns
-the number of objects read. 
-\end{itemize}
-This concludes the definitions tag.
+After investing a considerable amount of time into finding bugs and ending up with nothing of use, we fell back to Google in an attempt to find at least some buggy programs we could use as test cases.
+By using the Google search engine, we used the following statement as our search criteria for finding buggy programs: "What's wrong with this Java code?".
+Without digging too far through the pages that Google returned, we evaluated all of the links from first page of returned search query, and selected the programs that would compile.
+As a result, we gathered 3 buggy programs that we could use, and while they may not be substantial in size or complexity, they are representative of Byteboy's potential user base: developers (of any skill level) who need to debug their Java programs.
+The programs range in functionality from a basic Binary Search implementation, to a Average calculator program, to a GUI ActionListener-based program.
 
-\section{Approach}
+\subsection{Results}
 
-This is where our approach will go. \\
+Discuss the actual outcome of the program runs.
 
-\section{Evaluation \& Observations}
+\subsection{Observations}
 
-This is where our evaluation \& observations will go. \\
+Discuss the outputted rules from Byteboy.
 
-\section{Related Work}
+\subsection{Limitations}
+
+Discuss the limitations of our work.
+
+\section{RELATED WORK}
 
@@
 
-\section{Conclusion \& Future Work}
+\section{CONCLUSION \& FUTURE WORK}
 
-This is where the conclusion goes. \\
+Byteman is a powerful tool for tracing and debugging Java programs by injecting code into running application methods, but currently lacks the luxuries of modern programming languages.
+This paper has presented Byteboy, a companion application suite for Byteman that includes a manual and semi-automatic rule generator, a fuzz test generator, and a VS Code language extension.
+Byteboy has shown that it can produce rules that may be of use to developers, but will require additional work towards refining and strengthening it's functionality.
 
-\section{Acknowledgments}
-
-Good night Springton, there will be no encores. \\
+Future work may be conducted on the instrumentation phase of our approach, as it would be interesting to consider the results of performing different dynamic analysis algorithms on the target program in an attempt to generate a more comprehensive set of Byteman rules.
+Additionally, more work will be done to improve the grammar file of the language extension, and it will hopefully be available for download via the Visual Studio Marketplace in the near future.
 
@@
 \bibitem{bytemanwebsite} 
-Byteman: Simplify Java tracing, monitoring and testing with Byteman,
+Byteman: Simplify Java tracing, monitoring and testing with Byteman.
 \\\texttt{http://byteman.jboss.org/}
@@
 Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
-\\\texttt{http://downloads.jboss.org/byteman/3.0.10/ProgrammersGuide.html}
+\\\texttt{http://downloads.jboss.org/byteman
+/3.0.10/ProgrammersGuide.html}
 
-\bibitem{yo}
+\bibitem{bytemanblog}
+Dinn, Andrew. (2011). A Byteman Tutorial. \\\textit{JBoss Developer}. Retrieved from: 
+\\\texttt{https://developer.jboss.org/wiki
+/ABytemanTutorial}
+
+\bibitem{yoman}
+Yeoman.
+\\\texttt{http://yeoman.io/}
+
+\bibitem{yocode}
 Yo Code - Extension Generator
-\\\texttt{https://code.visualstudio.com/docs/extensions/yocode}
+\\\texttt{https://code.visualstudio.com/docs
+/extensions/yocode}
+
+\bibitem{bytemanextension}
+Byteman Language Extension.
+\\\texttt{https://github.com/aptmac/byteboy
+/tree/master/byteman-language-extension}
 
@@
 Textmate: Language Grammars
-\\\texttt{https://manual.macromates.com/en/language\_grammars}
+\\\texttt{https://manual.macromates.com/en
+/language\_grammars}
 

### 2017-12-06 analysis.py
anaylsis curently can find arugment methods and names, just need to merge to two into the rankings list

@@ -25,11 +25,13 @@ def run_analysis(java_file_path):
     # Runs the profiler on the provided java class
     # ranked methods by time (5 to 10)
     # Need its method name, CPU usage,  arguments, argmuent types, whats calling it (stack trace),
-    # TODO: figure out argument/agrument types
     if os.path.exists(java_file_path):        
         # check to see if it is a relative path or if there is something there already
         fullpath =  os.path.realpath(java_file_path)  
-        print "Analyzing..."
+        javap_result = subprocess.check_output("javap -p -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath), shell=True)
+        print javap_result
+        methods_with_arugments = re.findall(r"(\w+\(.*\))", javap_result)
+        print methods_with_arugments
         os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath))
         # Reads in the results, dumps some of it to the console
         results = open("./java.hprof.txt", "r")
@@ -65,7 +67,5 @@ def run_analysis(java_file_path):
                             break
         print rankings
         print "Analysis done. Check for arguments..."
-        javap_result = subprocess.check_output("javap -p -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath), shell=True)
-        print javap_result
     else:
         print ("Java file does not exist.")

### 2017-12-06 analysis.py
fix(analysis): fixed pathing for running java programs using a path

@@ -1,4 +1,4 @@
-#!/usr/bin/python3
+#!/usr/bin/python
 
 # analysis.py
 # CMPT 479 - Final Project
@@ -28,11 +28,15 @@ def run_analysis(java_file_path):
     if os.path.exists(java_file_path):        
         # check to see if it is a relative path or if there is something there already
         fullpath =  os.path.realpath(java_file_path)  
-        javap_result = subprocess.check_output("javap -p -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath), shell=True)
-        print javap_result
+        classpath = ''
+        if ".java" in os.path.basename(fullpath):
+            classpath = (os.path.basename(fullpath)).replace('.java', '')
+        elif ".class" in os.path.basename(fullpath):
+            classpath = (os.path.basename(fullpath)).replace('.class', '')
+        javap_result = subprocess.check_output("javap -p -classpath " + os.path.dirname(fullpath) + " " + classpath, shell=True)
         methods_with_arugments = re.findall(r"(\w+\(.*\))", javap_result)
-        print methods_with_arugments
-        os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + os.path.basename(fullpath))
+        print(methods_with_arugments)
+        os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + classpath)
         # Reads in the results, dumps some of it to the console
         results = open("./java.hprof.txt", "r")
         rankings = list()
@@ -65,7 +69,7 @@ def run_analysis(java_file_path):
                         else:
                             search_index += 1
                             break
-        print rankings
-        print "Analysis done. Check for arguments..."
+        print(rankings)
+        print("Analysis done. Check for arguments...")
     else:
-        print ("Java file does not exist.")
+        print("Java file does not exist.")

### 2017-12-06 main.py

@@ -1,4 +1,4 @@
-#!/usr/bin/python3
+#!/usr/bin/python
 
 # main.py
 # CMPT 479 - Final Project

### 2017-12-06 interactive.py
feat(interactive): manual creation is finished, writes rules to an output folder

@@ -1,4 +1,4 @@
-#!/usr/bin/python3
+#!/usr/bin/python
 
 # interactive.py
 # CMPT 479 - Final Project
@@ -12,75 +12,89 @@
 import os
 import sys
 
-#######################################################
-# TODO
-# ----
-# Idea: Create an array/list for the rule attributes
-#       So it can be easily edited if a mistake occurs
-
 ###
 # Helper Functions for adding content to Byteman Scripts
 ###
 
+# Appends the Rule name to the script
 def add_rule(script, rule_name):
     script += "RULE "
     script += rule_name
     script += "\n"
     return script
 
+# Appends the Class name to the script
 def add_class(script, class_name):
     script += "CLASS "
     script += class_name
     script += "\n"
     return script
 
+# Appends the Method name to the script
 def add_method(script, method_name):
     script += "METHOD "
     script += method_name
     script += "\n"
     return script
 
+# Appends the entry point to the script
+def add_entry(script, entry_point):
+    script += "AT "
+    script += entry_point
+    script += "\nIF TRUE\n"
+    return script
+
+# Appends the Rule Logic to the script
 def add_body(script, body):
     script += body
     return script
 
+def write_to_file(script):
+    filename = raw_input ("What would you like to call your file?: ")
+    if filename.find(".btm") == -1:
+        filename += ".btm"
+    if not os.path.exists("output"):
+        os.makedirs("output")
+    file = open("output/" + filename, "w")
+    file.write(script)
+    file.close()
+
+# Appends the ENDRULE keyword to the script 
 def add_endrule(script):
     script += "ENDRULE"
     return script
 
-###
-# Helper Functions for Guided and User-Controlled Script Writing
-###
-def create_guided_rule():
-    # Have it just create an advanced rule, for now.
-    create_advanced_rule()
-    return
 
-def create_advanced_rule():
+def manual_creation():
+    print("GUIDED MANUAL RULE CREATION")
     script = ""
     # Create a generic rule based completely on user input
-    script = add_rule(script, input("What is the rule name: "))
-    script = add_class(script, input("What is the target Class name: "))
-    script = add_method(script, input("What is the target Method name: "))
+    script = add_rule(script, raw_input("What would you like to name your Rule: "))
+    script = add_class(script, raw_input("What is the target Class name: "))
+    script = add_method(script, raw_input("What is the target Method name: "))
+    script = add_entry(script, raw_input("When would you like to trigger activity? (ENTRY or EXIT): "))
[…]

### 2017-12-06 interactive.py
chore(interactive): cleaned up some code and added more comments, added better prompts

@@ -18,30 +18,26 @@ import sys
 
 # Appends the Rule name to the script
 def add_rule(script, rule_name):
-    script += "RULE "
-    script += rule_name
-    script += "\n"
+    script += "RULE " + rule_name + "\n"
     return script
 
 # Appends the Class name to the script
 def add_class(script, class_name):
-    script += "CLASS "
-    script += class_name
-    script += "\n"
+    script += "CLASS " + class_name + "\n"
     return script
 
 # Appends the Method name to the script
 def add_method(script, method_name):
-    script += "METHOD "
-    script += method_name
-    script += "\n"
+    script += "METHOD " + method_name + "\n"
     return script
 
 # Appends the entry point to the script
 def add_entry(script, entry_point):
-    script += "AT "
-    script += entry_point
-    script += "\nIF TRUE\n"
+    script += "AT " + entry_point + "\n"
+    return script
+
+def add_conditional(script, condition):
+    script += "IF " + condition + "\n"
     return script
 
 # Appends the Rule Logic to the script
@@ -49,6 +45,13 @@ def add_body(script, body):
     script += body
     return script
 
+# Appends the ENDRULE keyword to the script 
+def add_endrule(script):
+    script += "ENDRULE"
+    return script
+
+# Writes the created rule to a file in the output folder, and creates
+# the output folder if it doesn't exist.
 def write_to_file(script):
     filename = raw_input ("What would you like to call your file?: ")
     if filename.find(".btm") == -1:
@@ -59,12 +62,10 @@ def write_to_file(script):
     file.write(script)
     file.close()
 
-# Appends the ENDRULE keyword to the script 
-def add_endrule(script):
-    script += "ENDRULE"
-    return script
-
-
+# Manual Creation()
+# - Guides the user through writing the necessary components of a Byteman rule
+# - Inspired by the Yeoman code generator, which offers similar functionality for
+# - - scaffolding JavaScript applications and VS Code extensions
 def manual_creation():
     print("GUIDED MANUAL RULE CREATION")
     script = ""
@@ -73,7 +74,8 @@ def manual_creation():
     script = add_class(script, raw_input("What is the target Class name: "))
     script = add_method(script, raw_input("What is the target Method name: "))
     script = add_entry(script, raw_input("When would you like to trigger activity? (ENTRY or EXIT): "))
-    print("What is the body of the script?: (input an empty line when finished)")
[…]

### 2017-12-06 analysis.py
anaylsis now will correctly spit out rankings list that will include its stack trace and the each methods arguement types, respectively.

@@ -44,7 +44,6 @@ def run_analysis(java_file_path):
 
         for line in results:                
             if "rank " in line:
-                #for entry in results:
                 for index, entry in enumerate(results):
                     if (index < TOTAL_RANKINGS):
                         temp_list = entry.split()
@@ -65,6 +64,11 @@ def run_analysis(java_file_path):
                         if ("TRACE " not in method):
                             method = re.sub(r'\t', '', method)
                             method = re.sub(r'\n', '', method)
+                            method_name = re.findall(r"(\w+)\(.*\)", method)
+                            for entry in methods_with_arugments:
+                                if method_name[0] in entry:
+                                    argument_type = re.findall(r"(\(.*\))", entry)
+                                    method = re.sub(r"\(.*\)", argument_type[0], method)
                             rankings[search_index].append(method)
                         else:
                             search_index += 1

### 2017-12-06 motivating-example/InfLoop.java

@@ -6,7 +6,8 @@ public class InfLoop {
         }
     }
 
-    private static void work() {}
+    private static void work() {
+    }
 
     public static void main(String[] args) { 
         InfLoop inf  = new InfLoop();

### 2017-12-06 analysis.py
removed a useless print statement that doesn't mean anything anymore

@@ -74,6 +74,5 @@ def run_analysis(java_file_path):
                             search_index += 1
                             break
         print(rankings)
-        print("Analysis done. Check for arguments...")
     else:
         print("Java file does not exist.")

### 2017-12-06 main.py
general housekeeping; removed random TODO comment on main that is of no use anymore

@@ -1,4 +1,4 @@
-#!/usr/bin/python
+#!/usr/bin/python3
 
 # main.py
 # CMPT 479 - Final Project

### 2017-12-06 interactive.py
feat(main.py): added cool ascii art, improved prompts, ability to run w/o program analysis part, and runs interactive.py functions

@@ -67,7 +67,9 @@ def write_to_file(script):
 # - Inspired by the Yeoman code generator, which offers similar functionality for
 # - - scaffolding JavaScript applications and VS Code extensions
 def manual_creation():
+    print("---------------------------")
     print("GUIDED MANUAL RULE CREATION")
+    print("---------------------------")
     script = ""
     # Create a generic rule based completely on user input
     script = add_rule(script, raw_input("What would you like to name your Rule: "))
@@ -104,10 +106,9 @@ def fuzztest_generator():
     return
 
 ####
-# Main
+# Main function of interactive.py
 ####
-def main():
-    os.system('clear')
+def interactive():
     print("-----------------------------------------------------")
     print("Welcome to the interactive Byteman script generator.")
     print("-----------------------------------------------------")
@@ -129,8 +130,3 @@ def main():
     elif result == 4:
         os.system("clear")
         fuzztest_generator()
-    print("Goodbye.")
-
-
-if __name__ == "__main__":
-    main()

### 2017-12-06 main.py

@@ -8,14 +8,39 @@ import os
 import sys
 
 from analysis import run_analysis
+from interactive import interactive
+from interactive import manual_creation
 
 def main(java_file):
-    
-    run_analysis(java_file)
+    os.system("clear")
+    print("Thanks for choosing")
+    # Cool ascii art courtesy of: http://www.patorjk.com/software/taag
+    print("______       _       _")         
+    print("| ___ \     | |     | |")                
+    print("| |_/ /_   _| |_ ___| |__   ___  _   _") 
+    print("| ___ \ | | | __/ _ \ '_ \ / _ \| | | |")
+    print("| |_/ / |_| | ||  __/ |_) | (_) | |_| |")
+    print("\____/ \__, |\__\___|_.__/ \___/ \__, |")
+    print("        __/ |                     __/ |")
+    print("       |___/                     |___/")
+    print("A Companion Application for Byteman.")
+    print("---------------------------------------")
+    print("- Running program analysis")
+    print("- - If program is stuck looping, use <ctrl+c> to continue")
+    if java_file != False:
+        run_analysis(java_file)
+        interactive()
+    else:
+        print("You have not supplied a Java application to Byteboy.")
+        print("The functionality available to you is Manual Rule Creation.")
+        result = raw_input("Do you wish to continue? (y/n): ")
+        if result == "y":
+            manual_creation()
+    print("Goodbye.")
 
 if __name__ == "__main__":
     try:
         java_file = sys.argv[1]
         main(java_file)
     except IndexError:
-        print("Invalid number of arguments supplied")
+        main(False)

### 2017-12-06 byteboy/analysis.py
feat(analysis): if supplied with a .java file, we will compile the program

@@ -30,6 +30,7 @@ def run_analysis(java_file_path):
         fullpath =  os.path.realpath(java_file_path)  
         classpath = ''
         if ".java" in os.path.basename(fullpath):
+            os.system('javac ' + str(fullpath))
             classpath = (os.path.basename(fullpath)).replace('.java', '')
         elif ".class" in os.path.basename(fullpath):
             classpath = (os.path.basename(fullpath)).replace('.class', '')

### 2017-12-06 byteboy/byteboy.py
chore(byteboy): added a readme for the python application

@@ -26,7 +26,7 @@ def main(java_file):
     print("A Companion Application for Byteman.")
     print("---------------------------------------")
     print("- Running program analysis")
-    print("- - If program is stuck looping, use <ctrl+c> to continue")
+    print("- - If you think the program is stuck looping, use <ctrl+c> to continue")
     if java_file != False:
         run_analysis(java_file)
         interactive()

### 2017-12-06 byteboy/analysis.py
chore(byteboy): addded return statements to the analysis function, updated interactive documentation

@@ -75,5 +75,6 @@ def run_analysis(java_file_path):
                             search_index += 1
                             break
         print(rankings)
+        return rankings, methods_with_arugments
     else:
         print("Java file does not exist.")

### 2017-12-06 byteboy/byteboy.py

@@ -28,8 +28,8 @@ def main(java_file):
     print("- Running program analysis")
     print("- - If you think the program is stuck looping, use <ctrl+c> to continue")
     if java_file != False:
-        run_analysis(java_file)
-        interactive()
+        rankings, methods  = run_analysis(java_file)
+        interactive(rankings, methods)
     else:
         print("You have not supplied a Java application to Byteboy.")
         print("The functionality available to you is Manual Rule Creation.")

### 2017-12-06 byteboy/interactive.py

@@ -97,18 +97,25 @@ def semiautomatic_creation():
     # TODO
     return
 
+# Automatic Generator()
+# - Using the results from the analysis, automatically generates rules that can be used
+# - - to trace application behaviour and progress
 def automatic_generator():
     # TODO
     return
 
-def fuzztest_generator():
+# Fuzztest Generation()
+# - Using the results of the analysis, figures out the data types of the arguments used
+# - - in the method's arguments, and replace the variable contents with different values
+# - - of the same type (or null)
+def fuzztest_generator(methods):
     # TODO
     return
 
 ####
 # Main function of interactive.py
 ####
-def interactive():
+def interactive(rankings, methods):
     print("-----------------------------------------------------")
     print("Welcome to the interactive Byteman script generator.")
     print("-----------------------------------------------------")
@@ -129,4 +136,4 @@ def interactive():
         automatic_generator()
     elif result == 4:
         os.system("clear")
-        fuzztest_generator()
+        fuzztest_generator(methods)

### 2017-12-06 byteboy/interactive.py
added additional skeleton code for automatic_generator() and semi-automatic_creation()

@@ -93,7 +93,12 @@ def manual_creation():
 # - Using the results from the analysis, functions similar to the manual creation
 # - - but suggests what Classes/Methods/etc. the user may be interested in
 # - - based on the execution of their program.
-def semiautomatic_creation():
+def semiautomatic_creation(rankings):
+    print("---------------------------")
+    print("GUIDED SEMIAUTOMATIC RULE CREATION")
+    print("---------------------------")
+    # Suggest rules that are found from our analysis
+    script = ""
     # TODO
     return
 
@@ -101,6 +106,11 @@ def semiautomatic_creation():
 # - Using the results from the analysis, automatically generates rules that can be used
 # - - to trace application behaviour and progress
 def automatic_generator():
+    print("---------------------------")
+    print("AUTOMATIC RULE CREATION - ALPHA")
+    print("---------------------------")
+    # Automatically generate rules (or try to) that are found from our analysis
+    script = ""
     # TODO
     return
 
@@ -130,7 +140,7 @@ def interactive(rankings, methods):
         manual_creation()
     elif result == 2:
         os.system("clear")
-        semiautomatic_creation()
+        semiautomatic_creation(rankings)
     elif result == 3:
         os.system("clear")
         automatic_generator()

### 2017-12-06 byteboy/interactive.py
fix(interactive): fixed an error where inputting a non-integer value as an option would cause a ValueError exception

@@ -134,16 +134,21 @@ def interactive(rankings, methods):
     print("3. Automatic Rule Generation (for tracing purposes)")
     print("4. Fuzz Test Generator")
     print("5. Exit")
-    result = int(input("Please select your choice: "))
-    if result == 1:
+    result = raw_input("Please select your choice: ")
+    try:
+      result = int(result)
+      if result == 1:
         os.system("clear")
         manual_creation()
-    elif result == 2:
+      elif result == 2:
         os.system("clear")
         semiautomatic_creation(rankings)
-    elif result == 3:
+      elif result == 3:
         os.system("clear")
         automatic_generator()
-    elif result == 4:
+      elif result == 4:
         os.system("clear")
         fuzztest_generator(methods)
+    except ValueError:
+        print("Invalid input.")
+        print("You must supply the number of the corresponding action you wish to perform.")

### 2017-12-07 byteboy/analysis.py
fixed issue with multiple methods that are in top 5

@@ -48,13 +48,15 @@ def run_analysis(java_file_path):
                 for index, entry in enumerate(results):
                     if (index < TOTAL_RANKINGS):
                         temp_list = entry.split()
-                        # check to see if the process is passing CPU usage threshold
-                        if (float(temp_list[SELF].strip("%")) >= THRESHOLD):
-                            trace_search_list.append("TRACE " + temp_list[TRACE] + ":") 
-                            # ignore method name as it will appear in stack trace and accum as they are not useful for diagnostic anymore
-                            del temp_list[METHOD]
-                            del temp_list[ACCUM]
-                            rankings.append(temp_list)
+                        # Do not include items that are internal java calls
+                        if ("java." in entry):
+                            break
+                        temp_list = entry.split()
+                        trace_search_list.append("TRACE " + temp_list[TRACE] + ":") 
+                        # ignore method name as it will appear in stack trace and accum as they are not useful for diagnostic anymore
+                        del temp_list[METHOD]
+                        del temp_list[ACCUM]
+                        rankings.append(temp_list)
                     else: break
         search_index = 0 
         for search_query in trace_search_list:

### 2017-12-07 byteboy/byteboy.py
chore(byteboy): moved println for message confirmation of running analysis into the correct part of the if-statement

@@ -25,9 +25,9 @@ def main(java_file):
     print("       |___/                     |___/")
     print("A Companion Application for Byteman.")
     print("---------------------------------------")
-    print("- Running program analysis")
-    print("- - If you think the program is stuck looping, use <ctrl+c> to continue")
     if java_file != False:
+        print("- Running program analysis")
+        print("- - If you think the program is stuck looping, use <ctrl+c> to continue")
         rankings, methods  = run_analysis(java_file)
         interactive(rankings, methods)
     else:

### 2017-12-07 byteboy/analysis.py
fixed some comment issues

@@ -19,11 +19,9 @@ def run_analysis(java_file_path):
     TRACE  = 4
     METHOD = 5
 
-    THRESHOLD = 20
-
     """returns a .txt file with analysis details for interactive"""
     # Runs the profiler on the provided java class
-    # ranked methods by time (5 to 10)
+    # ranked methods by time (5)
     # Need its method name, CPU usage,  arguments, argmuent types, whats calling it (stack trace),
     if os.path.exists(java_file_path):        
         # check to see if it is a relative path or if there is something there already

### 2017-12-07 byteboy/analysis.py
fixed some comment issues

@@ -22,7 +22,7 @@ def run_analysis(java_file_path):
     """returns a .txt file with analysis details for interactive"""
     # Runs the profiler on the provided java class
     # ranked methods by time (5)
-    # Need its method name, CPU usage,  arguments, argmuent types, whats calling it (stack trace),
+    # Need its method name, CPU usage,  arguments, argmuent types, and whats calling it (stack trace)
     if os.path.exists(java_file_path):        
         # check to see if it is a relative path or if there is something there already
         fullpath =  os.path.realpath(java_file_path)  

### 2017-12-07 byteboy/analysis.py
feat(fuzz): added functionality for a basic fuzz test generator

@@ -77,6 +77,20 @@ def run_analysis(java_file_path):
                             search_index += 1
                             break
         print(rankings)
-        return rankings, methods_with_arugments
+        return rankings, methods_with_arugments, classpath
     else:
         print("Java file does not exist.")
+
+# Function to regex to get the variables out of the method declaration as a string
+def parse_variables(fn):
+    vars_re = re.compile(".*\((.*?)\)")
+    m = vars_re.match(fn)
+    vars_string = m.group(1).replace(" ", "")
+    vars_list = vars_string.split(",")
+    return vars_list
+
+# Given a function declaration, return the function name
+def get_method_name(method):
+    method_re = re.compile("^(.*)\(")
+    m = method_re.match(method)
+    return m.group(1)

### 2017-12-07 byteboy/byteboy.py

@@ -28,8 +28,8 @@ def main(java_file):
     if java_file != False:
         print("- Running program analysis")
         print("- - If you think the program is stuck looping, use <ctrl+c> to continue")
-        rankings, methods  = run_analysis(java_file)
-        interactive(rankings, methods)
+        rankings, methods, classname  = run_analysis(java_file)
+        interactive(rankings, methods, classname)
     else:
         print("You have not supplied a Java application to Byteboy.")
         print("The functionality available to you is Manual Rule Creation.")

### 2017-12-07 byteboy/interactive.py

@@ -10,7 +10,12 @@
 # If Byteman is configured on the host's machine, should allow for syntax checking as well.
 
 import os
+import random
+import uuid
 import sys
+
+from analysis import parse_variables
+from analysis import get_method_name
 
 ###
 # Helper Functions for adding content to Byteman Scripts
@@ -50,10 +55,46 @@ def add_endrule(script):
     script += "ENDRULE"
     return script
 
+####
+# Helper functions to fuzz random values
+####
+def fuzz_int():
+    max_int = 2147483647
+    return random.randint(-max_int, max_int)
+
+def fuzz_long():
+    max_long = 9223372036854775807
+    return random.randint(-max_long, max_long)
+
+def fuzz_float():
+    modifier = random.uniform(0, 1)
+    return modifier*fuzz_long()
+
+def fuzz_double():
+    return fuzz_float()
+
+def fuzz_string():
+    # Idea to use uuid borrowed from StackOverflow discussion found at:
+    # https://stackoverflow.com/questions/37675280/how-to-generate-a-random-string
+    return "\"{}\"".format(uuid.uuid4().hex)
+
+def fuzz_boolean():
+    if random.randint(0, 10) > 5:
+        return "true"
+    else:
+        return "false"
+
+def fuzz_action(script, pos, value):
+    script += "DO\n"
+    action = "${} = {}\n".format(pos, value)
+    script += action
+    return script
+
 # Writes the created rule to a file in the output folder, and creates
 # the output folder if it doesn't exist.
-def write_to_file(script):
-    filename = raw_input ("What would you like to call your file?: ")
+def write_to_file(script, filename = False):
+    if filename == False:
+        filename = raw_input ("What would you like to call your file?: ")
     if filename.find(".btm") == -1:
         filename += ".btm"
     if not os.path.exists("output"):
@@ -93,7 +134,7 @@ def manual_creation():
 # - Using the results from the analysis, functions similar to the manual creation
 # - - but suggests what Classes/Methods/etc. the user may be interested in
 # - - based on the execution of their program.
-def semiautomatic_creation(rankings):
+def semiautomatic_creation(rankings, classname):
     print("---------------------------")
     print("GUIDED SEMIAUTOMATIC RULE CREATION")
     print("---------------------------")
@@ -105,7 +146,7 @@ def semiautomatic_creation(rankings):
 # Automatic Generator()
 # - Using the results from the analysis, automatically generates rules that can be used
 # - - to trace application behaviour and progress
[…]

### 2017-12-07 byteboy/analysis.py
chore(analysis): added description to what each println to the console does

@@ -34,7 +34,7 @@ def run_analysis(java_file_path):
             classpath = (os.path.basename(fullpath)).replace('.class', '')
         javap_result = subprocess.check_output("javap -p -classpath " + os.path.dirname(fullpath) + " " + classpath, shell=True)
         methods_with_arugments = re.findall(r"(\w+\(.*\))", javap_result)
-        print(methods_with_arugments)
+        print("Found methods: " + str(methods_with_arugments))
         os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + classpath)
         # Reads in the results, dumps some of it to the console
         results = open("./java.hprof.txt", "r")
@@ -74,7 +74,7 @@ def run_analysis(java_file_path):
                         else:
                             search_index += 1
                             break
-        print(rankings)
+        print("Rankings: " + str(rankings))
         return rankings, methods_with_arugments, classpath
     else:
         print("Java file does not exist.")

### 2017-12-07 byteboy/interactive.py
feat(tracing): added functionality to generate a set of rules that will trace the source program

@@ -135,9 +135,9 @@ def manual_creation():
 # - - but suggests what Classes/Methods/etc. the user may be interested in
 # - - based on the execution of their program.
 def semiautomatic_creation(rankings, classname):
-    print("---------------------------")
+    print("----------------------------------")
     print("GUIDED SEMIAUTOMATIC RULE CREATION")
-    print("---------------------------")
+    print("----------------------------------")
     # Suggest rules that are found from our analysis
     script = ""
     # TODO
@@ -146,13 +146,39 @@ def semiautomatic_creation(rankings, classname):
 # Automatic Generator()
 # - Using the results from the analysis, automatically generates rules that can be used
 # - - to trace application behaviour and progress
-def automatic_generator(classname):
-    print("---------------------------")
-    print("AUTOMATIC RULE CREATION - ALPHA")
-    print("---------------------------")
+def automatic_generator(methods, classname):
+    print("---------------------------------")
+    print("AUTOMATIC RULE CREATION - Tracing")
+    print("---------------------------------")
     # Automatically generate rules (or try to) that are found from our analysis
-    script = ""
-    # TODO
+    files = []
+    for method in methods:
+        method = get_method_name(method)
+        script = ''
+        # Generate the Entry Rule
+        script = add_rule(script, "Traceln when Entering {}.{}".format(classname, method))
+        script = add_class(script, classname)
+        script = add_method(script, method)
+        script = add_entry(script, "ENTRY")
+        script = add_conditional(script, "TRUE")
+        script += "DO\ntraceln(\"- Entering {} in class {}\")\n".format(method, classname)
+        script = add_endrule(script)
+        script += "\n\n"
+
+        # Generate the Exit Rule
+        script = add_rule(script, "Traceln when Exiting {}.{}".format(classname, method))
+        script = add_class(script, classname)
+        script = add_method(script, method)
+        script = add_entry(script, "EXIT")
+        script = add_conditional(script, "TRUE")
+        script += "DO\ntraceln(\"- Exiting {} in class {}\")\n".format(method, classname)
+        script = add_endrule(script)
+
+        # Write to file
+        filename = "trace_{}-{}".format(classname, method)
+        files.append(filename)
+        write_to_file(script, filename)
+    print("The following set of files have been created: " + str(files))
     return
 
 # Fuzztest Generation()
@@ -160,6 +186,9 @@ def automatic_generator(classname):
 # - - in the method's arguments, and replace the variable contents with different values
 # - - of the same type (or null)
 def fuzztest_generator(methods, classname):
[…]

### 2017-12-07 byteboy/byteboy.py
feat(prog.loop): added a loop so the user can continue to use Byteboy after completing an action

@@ -10,19 +10,12 @@ import sys
 from analysis import run_analysis
 from interactive import interactive
 from interactive import manual_creation
+from interactive import print_ascii_art
 
 def main(java_file):
     os.system("clear")
     print("Thanks for choosing")
-    # Cool ascii art courtesy of: http://www.patorjk.com/software/taag
-    print("______       _       _")         
-    print("| ___ \     | |     | |")                
-    print("| |_/ /_   _| |_ ___| |__   ___  _   _") 
-    print("| ___ \ | | | __/ _ \ '_ \ / _ \| | | |")
-    print("| |_/ / |_| | ||  __/ |_) | (_) | |_| |")
-    print("\____/ \__, |\__\___|_.__/ \___/ \__, |")
-    print("        __/ |                     __/ |")
-    print("       |___/                     |___/")
+    print_ascii_art()
     print("A Companion Application for Byteman.")
     print("---------------------------------------")
     if java_file != False:

### 2017-12-07 byteboy/interactive.py

@@ -230,31 +230,54 @@ def fuzztest_generator(methods, classname):
     print("The following set of files have been created: " + str(files))
     return
 
+def print_ascii_art():
+    # Cool ascii art courtesy of: http://www.patorjk.com/software/taag
+    print("______       _       _")         
+    print("| ___ \     | |     | |")                
+    print("| |_/ /_   _| |_ ___| |__   ___  _   _") 
+    print("| ___ \ | | | __/ _ \ '_ \ / _ \| | | |")
+    print("| |_/ / |_| | ||  __/ |_) | (_) | |_| |")
+    print("\____/ \__, |\__\___|_.__/ \___/ \__, |")
+    print("        __/ |                     __/ |")
+    print("       |___/                     |___/")
+
 ####
 # Main function of interactive.py
 ####
 def interactive(rankings, methods, classname):
-    print("-----------------------------------------------------")
-    print("Welcome to the interactive Byteman script generator.")
-    print("-----------------------------------------------------")
-    print("1. Manual Rule Creation")
-    print("2. Semi-Automatic Rule Creation")
-    print("3. Automatic Rule Generation (for tracing purposes)")
-    print("4. Fuzz Test Generator")
-    print("5. Exit")
-    result = raw_input("Please select your choice: ")
-    try:
-      result = int(result)
-      if result == 1:
-        os.system("clear")
-        manual_creation()
-      elif result == 2:
-        os.system("clear")
-        semiautomatic_creation(rankings, classname)
-      elif result == 3:
-        automatic_generator(methods, classname)
-      elif result == 4:
-        fuzztest_generator(methods, classname)
-    except ValueError:
-        print("Invalid input.")
-        print("You must supply the number of the corresponding action you wish to perform.")
+    cont = 0
+    while(cont == 0):
+        print("-----------------------------------------------------")
+        print("Welcome to the interactive Byteman script generator.")
+        print("-----------------------------------------------------")
+        print("1. Manual Rule Creation")
+        print("2. Semi-Automatic Rule Creation")
+        print("3. Automatic Rule Generation (for tracing purposes)")
+        print("4. Fuzz Test Generator")
+        print("5. Exit")
+        result = raw_input("Please select your choice: ")
+        try:
+            result = int(result)
+            if result == 1:
+                os.system("clear")
+                manual_creation()
+            elif result == 2:
+                os.system("clear")
+                semiautomatic_creation(rankings, classname)
+            elif result == 3:
+                automatic_generator(methods, classname)
+            elif result == 4:
[…]

### 2017-12-07 byteboy/byteboy.py
feat(semi-auto): added base functionality for a guided rule creation option

@@ -29,7 +29,7 @@ def main(java_file):
         result = raw_input("Do you wish to continue? (y/n): ")
         if result == "y":
             manual_creation()
-    print("Goodbye.")
+    print("Thank you for using Byteboy.\nHave a nice day!")
 
 if __name__ == "__main__":
     try:

### 2017-12-07 byteboy/interactive.py

@@ -94,7 +94,7 @@ def fuzz_action(script, pos, value):
 # the output folder if it doesn't exist.
 def write_to_file(script, filename = False):
     if filename == False:
-        filename = raw_input ("What would you like to call your file?: ")
+        filename = raw_input ("What would you like to call your rule file? (e.g., <name>.btm): ")
     if filename.find(".btm") == -1:
         filename += ".btm"
     if not os.path.exists("output"):
@@ -128,19 +128,51 @@ def manual_creation():
     script = add_body(script, body)
     script = add_endrule(script)
     write_to_file(script)
+    print("Manual Creation has completed.")
     return
 
 # Semiautomatic Creation()
 # - Using the results from the analysis, functions similar to the manual creation
 # - - but suggests what Classes/Methods/etc. the user may be interested in
 # - - based on the execution of their program.
-def semiautomatic_creation(rankings, classname):
+def semiautomatic_creation(methods, classname):
     print("----------------------------------")
     print("GUIDED SEMIAUTOMATIC RULE CREATION")
     print("----------------------------------")
-    # Suggest rules that are found from our analysis
+    print("INSTRUCTIONS")
+    print("- Based on the analysis results, Byteboy will list potential options you may be interested in.")
+    print("- Feel free to use the highest ranking option, or if you type nothing then Byteboy will automatically use the first entry.")
+    print("- Let's begin!\n")
     script = ""
-    # TODO
+    print("The identified CLASS name is: " + classname)
+    method = raw_input("The identified METHODS are:\n" + str(methods) + "\nWhich METHOD do you wish to target? (only enter the name): ")
+    if method == "":
+        method = get_method_name(methods[0])
+    entry = raw_input("When would you like to trigger activity? (ENTRY/EXIT, default is ENTRY): ")
+    if entry == "":
+        entry = "ENTRY"
+    condition = raw_input("Under what conditions should the rule execute? (default is IF TRUE): ")
+    if condition == "":
+        condition = "TRUE"
+    print("What is the body of the script? (input an empty line when finished):\n- For Example: traceln(\"<text>\") could be used to write text to the console.")
+    body = "DO\n"
+    while True:
+        line = raw_input()
+        if not line: break
+        body += line
+        body += "\n"
+    rulename = raw_input("What would you like to name your rule?: ")
+
+    # Compile the rule & write to file
+    script = add_rule(script, rulename)
+    script = add_class(script, classname)
+    script = add_method(script, method)
+    script = add_entry(script, entry)
[…]

### 2017-12-07 byteboy/interactive.py
fix(auto-gen.): fix a bug where Byteboy generates a rule for the class as if it were a function

@@ -186,6 +186,8 @@ def automatic_generator(methods, classname):
     files = []
     for method in methods:
         method = get_method_name(method)
+        if method == classname:
+            break # don't want to write a rule for the class declaration
         script = ''
         # Generate the Entry Rule
         script = add_rule(script, "Traceln when Entering {}.{}".format(classname, method))

### 2017-12-07 byteboy/interactive.py
fix(auto-gen.): re-fixes the problem of creating a rule that targets class instead of function

@@ -186,32 +186,31 @@ def automatic_generator(methods, classname):
     files = []
     for method in methods:
         method = get_method_name(method)
-        if method == classname:
-            break # don't want to write a rule for the class declaration
-        script = ''
-        # Generate the Entry Rule
-        script = add_rule(script, "Traceln when Entering {}.{}".format(classname, method))
-        script = add_class(script, classname)
-        script = add_method(script, method)
-        script = add_entry(script, "ENTRY")
-        script = add_conditional(script, "TRUE")
-        script += "DO\ntraceln(\"- Entering {} in class {}\")\n".format(method, classname)
-        script = add_endrule(script)
-        script += "\n\n"
+        if method != classname:  # don't want to write a rule for the class declaration
+            script = ''
+            # Generate the Entry Rule
+            script = add_rule(script, "Traceln when Entering {}.{}".format(classname, method))
+            script = add_class(script, classname)
+            script = add_method(script, method)
+            script = add_entry(script, "ENTRY")
+            script = add_conditional(script, "TRUE")
+            script += "DO\ntraceln(\"- Entering {} in class {}\")\n".format(method, classname)
+            script = add_endrule(script)
+            script += "\n\n"
 
-        # Generate the Exit Rule
-        script = add_rule(script, "Traceln when Exiting {}.{}".format(classname, method))
-        script = add_class(script, classname)
-        script = add_method(script, method)
-        script = add_entry(script, "EXIT")
-        script = add_conditional(script, "TRUE")
-        script += "DO\ntraceln(\"- Exiting {} in class {}\")\n".format(method, classname)
-        script = add_endrule(script)
+            # Generate the Exit Rule
+            script = add_rule(script, "Traceln when Exiting {}.{}".format(classname, method))
+            script = add_class(script, classname)
+            script = add_method(script, method)
+            script = add_entry(script, "EXIT")
+            script = add_conditional(script, "TRUE")
+            script += "DO\ntraceln(\"- Exiting {} in class {}\")\n".format(method, classname)
+            script = add_endrule(script)
 
-        # Write to file
-        filename = "trace_{}-{}".format(classname, method)
-        files.append(filename)
-        write_to_file(script, filename)
+            # Write to file
+            filename = "trace_{}-{}".format(classname, method)
+            files.append(filename)
+            write_to_file(script, filename)
     print("The following set of files have been created: " + str(files))
     print("Automatic Generation has completed.")
     return

### 2017-12-07 final-paper/paper.la_.tex
feat(paper): added results section

@@
 As a result, we gathered 3 buggy programs that we could use, and while they may not be substantial in size or complexity, they are representative of Byteboy's potential user base: developers (of any skill level) who need to debug their Java programs.
-The programs range in functionality from a basic Binary Search implementation, to a Average calculator program, to a GUI ActionListener-based program.
+The programs range in functionality from a basic Binary Search implementation, to an average marks calculator program, to a GUI ActionListener-based program.
 
@@
 
-Discuss the actual outcome of the program runs.
+This section will focus on the outcomes of running the automatic rule generation and fuzz test generation functionality on the test programs.
+The following table showcases Byteboy's ability to create valid rules based on the selected action:
+\begin{center}
+ \begin{tabular}{||c | c | c||} 
+ \hline
+ Program & Auto. Generator & Fuzz Test Generator\\ [0.5ex] 
+ \hline\hline
+ A & Yes & Yes\\ 
+ \hline
+ BinarySearch & Yes & No\\
+ \hline
+ InfLoop & Yes & Yes\\
+ \hline
+ Question3 & Yes & Yes\\ [1ex] 
+ \hline
+\end{tabular}
+\end{center}
+
+In all cases, Byteboy was able to create a set of rules which provided tracing functionality for the given program.
+These traces outlined the current program behaviour, and could be of use to detect control flow errors, or unexpected program behaviour.
+
+In all but one case ({\tt BinarySearch.java}), Byteboy was able to produce a set of rules which could be used to potentially alter program behaviour.
+For the most part, these rules had little affect on the program's execution, which means that the program is robust enough to deal with unexpected input.
+In the case of {\tt InfLoop.java}, the generated test actually caused the previously infinite loop to exit, ceasing execution of the program.
+While we are pleased with the initial results of the fuzz test generator functionality, there are many cases that cannot be properly handled, and we will explain these situations in the Limitations part of this paper.
 

### 2017-12-07 final-paper/paper.la_.tex
feat(paper): added observations section

@@
 %make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Byteboy : A Byteman Companion Application}
+\title{\Large \bf Byteboy : A Byteman Companion application}
 
@@
 
-In this paper, we propose Byteboy, a companion application for Byteman.
+In this paper, we propose Byteboy\cite{byteboy}, a companion application for Byteman.
 Byteboy provides functionality for manual and semi-automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension.
@@
 
-Discuss the outputted rules from Byteboy.
+Each of the four programs were able to have at least some sort of their execution behaviour traced by using the set of rules which were automatically generated by Byteboy.
+The majority of the four program's don't exhibit complex function interactions, so the traceln results aren't as verbose as they could be in an application of larger scale.
+However, for an average developer looking to see where their program may be getting into trouble, these generated rules should be of some use.
+
+The fuzz test rules varied in their range of effectiveness, and their results will be explained individually.
+
+    {\tt A.java}: In the case of this program, the variable supplied to the {\tt A()} function is passed into a constructor for {\tt JFrame()}, and as a result, substituting the value of this variable has little to no effect on the application's behaviour.
+In this case, the fuzz test rule works only in the sense that it can be run and changes the title of the produced JFrame, but has no effect on the rest of the program's execution.
+
+{\tt InfLoop.java}: In this program, an infinite loop is entered because the {\tt doWork()} function gets passed a variable with the value of 0, which causes a while loop to start.
+This while loop has no exit condition, and as a result, the program loops forever.
+Fortunately, the fuzz test re-assigns the value of the variable which the loop in {\tt doWork()} evaluates in order to start looping.
+In the case that the fuzz test generates the value of 0, then the program will infinitely loop as previous.
+However, it is highly likely that a non-zero value will be produced from the fuzz test randomizer, which will allow the program to bypass the infinite loop completly, thus ceasing execution of the program.
+
+{\tt Question3.java}: This program accepts 10 integers as input, and attempts to calculate the average.
+The fuzz test generator targets the function responsible for calculating the average, but unfortunately the program throws an {\tt ArrayOutOfBoundsException} and crashes before the fuzzed value can be substituted.
+Unfortunately, the generated fuzz test rules will not have a chance to operate in this example, because of the nature of the error.
 
@@
 
+\bibitem{byteboy}
+Byteboy.
+\\\texttt{https://github.com/aptmac/byteboy}
+
 \end{thebibliography}

### 2017-12-07 byteboy/interactive.py
fix(fuzz): fixed a bug that would exit the rule creation loop if encountering an unsupported data type

@@ -234,33 +234,33 @@ def fuzztest_generator(methods, classname):
         if len(variables) >= 1:
             i = 1
             for var in variables:
-              value = ""
-              if var == "int":
-                  value = fuzz_int()
-              elif var == "long":
-                  value = fuzz_long()
-              elif var == "float":
-                  value = fuzz_float()
-              elif var == "double":
-                  value = fuzz_double()
-              elif var == "boolean":
-                  value = fuzz_boolean()
-              elif var == "java.lang.String":
-                  value = fuzz_string()
-              else: break  
-              # Generate the rule
-              script = ''
-              script = add_rule(script, "Fuzz {}.{}() parameter #{} of type {}".format(classname, method, i, var))
-              script = add_class(script, classname)
-              script = add_method(script, method)
-              script = add_entry(script, "ENTRY")
-              script = add_conditional(script, "TRUE")
-              script = fuzz_action(script, i, value)
-              script = add_endrule(script)
-              filename = "fuzz_{}-{}_arg{}-{}".format(classname, method, i, var)
-              files.append(filename)
-              write_to_file(script, filename)
-              i = i + 1
+                value = ""
+                if var == "int":
+                    value = fuzz_int()
+                elif var == "long":
+                    value = fuzz_long()
+                elif var == "float":
+                    value = fuzz_float()
+                elif var == "double":
+                    value = fuzz_double()
+                elif var == "boolean":
+                    value = fuzz_boolean()
+                elif var == "java.lang.String":
+                    value = fuzz_string()
+                else: continue
+                # Generate the rule
+                script = ''
+                script = add_rule(script, "Fuzz {}.{}() parameter #{} of type {}".format(classname, method, i, var))
+                script = add_class(script, classname)
+                script = add_method(script, method)
+                script = add_entry(script, "ENTRY")
+                script = add_conditional(script, "TRUE")
+                script = fuzz_action(script, i, value)
+                script = add_endrule(script)
+                filename = "fuzz_{}-{}_arg{}-{}".format(classname, method, i, var)
+                files.append(filename)
+                write_to_file(script, filename)
+                i = i + 1
     print("The following set of files have been created: " + str(files))
     print("Fuzz Test Generation has completed.")
     return

### 2017-12-07 final-paper/paper.la_.tex
fix(paper): updated results and observations section

@@
  \hline
- BinarySearch & Yes & No\\
+ BinarySearch & Yes & Yes\\
  \hline
@@
 
-In all but one case ({\tt BinarySearch.java}), Byteboy was able to produce a set of rules which could be used to potentially alter program behaviour.
+In all cases, Byteboy was able to produce a set of rules which could be used to potentially alter program behaviour.
 For the most part, these rules had little affect on the program's execution, which means that the program is robust enough to deal with unexpected input.
@@
 In this case, the fuzz test rule works only in the sense that it can be run and changes the title of the produced JFrame, but has no effect on the rest of the program's execution.
+
+{\tt BinarySearch.java}: This program has a bug in the way it outputs it's results, and while the execution is able to sustain the fuzz test randomized values, the effect on program behaviour cannot be observed.
 

### 2017-12-07 byteboy/analysis.py
added Report feature to show some information about the rankings include count and CPU%

@@ -34,7 +34,6 @@ def run_analysis(java_file_path):
             classpath = (os.path.basename(fullpath)).replace('.class', '')
         javap_result = subprocess.check_output("javap -p -classpath " + os.path.dirname(fullpath) + " " + classpath, shell=True)
         methods_with_arugments = re.findall(r"(\w+\(.*\))", javap_result)
-        print("Found methods: " + str(methods_with_arugments))
         os.system("java -agentlib:hprof=cpu=times -classpath " + os.path.dirname(fullpath) + " " + classpath)
         # Reads in the results, dumps some of it to the console
         results = open("./java.hprof.txt", "r")
@@ -74,7 +73,11 @@ def run_analysis(java_file_path):
                         else:
                             search_index += 1
                             break
-        print("Rankings: " + str(rankings))
+        print("Analysis complete.\n")
+        print("REPORT")
+        for entry in rankings:
+            print ("Method "+entry[4]+" was called "+entry[2]+" times using "+entry[1]+" CPU.")
+        print("\n")
         return rankings, methods_with_arugments, classpath
     else:
         print("Java file does not exist.")

### 2017-12-08 final-paper/paper.la_.tex
Added Instrumentation and Analysis sections

@@
 {\rm Ian Pun}\\
+ipun[at]sfu.ca\\
 Simon Fraser University
@@
 
-This is where we discuss hprof.
+In order for us to discover useful information in our Java application, we opted to use HProf.
+As a JVM native agent library, HPROF is dynamically loaded through a command line option, at JVM startup, and becomes part of the JVM process\cite{hprof}.
+This allows users to request relevant information such as CPU usage, method calls and their call frequency, and their stack traces.
+The results are then ranked, parsed, and organized through the analysis phase.
 
@@
 
-This is where we discuss the Python application and why we used Python.
+Majority of the work required for Byteboy is analysing the results from HPROF and presenting it back to the reader in a useful manner.
+We decided to use Python to handle this task as it was the most accessable and lightweight language available.
+
+Byteboy uses HPROF to generate a {\tt java.hprof.txt} file after the Java application completes its run.
+It handles applications with an infinite loop by instructing the user to use the {\tt Ctrl+C} shortcut to terminate the process.
+This will still generate the proper {\tt java.hprof.txt} file which Byteboy will interpret.
+The resulting {\tt java.hprof.txt} file gives us information of all the methods called in the JVM, their call count, CPU usage, and their stack traces.
+Byteboy will only use the top 5 method calls that are not internal java libraries with the most CPU usage for its semi-automatic, automatic, and fuzzer features.
+
+Unfortunately, HPROF does not generate information about method argument types, which is necessary in order to include fuzzer functionality.
+{\tt Javap} is a Java class file disassembler that can print out the package, protected, and public fields and methods passed into it\cite{javap}.
+Using Javap, we are able to create an additional analysis of the java application which strictly gives us method argument types.
+Byteboy will then combine the outputs of HPROF and {\tt javap} in order to produce the top 5 method calls and their respective argument types.
 
@@
 
+\bibitem{hprof}
+HPROF: A Heap/CPU Profiling Tool
+\\\texttt{https://docs.oracle.com/javase/7/docs/technotes
+/samples/hprof.html}
+
+\bibitem{javap}
+javap - The Java Class File Disassembler
+\\\texttt{https://docs.oracle.com/javase/7/docs/technotes
+/tools/windows/javap.html}
+
 \end{thebibliography}

### 2017-12-08 final-paper/paper.la_.tex
fix(paper): fixed reference formatting so the cite numbers appear in generated pdf

@@
 Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
-\\\texttt{http://downloads.jboss.org/byteman
-/3.0.10/ProgrammersGuide.html}
+\\\texttt{http://downloads.jboss.org/byteman/\newline3.0.10/ProgrammersGuide.html}
 
 \bibitem{bytemanblog}
-Dinn, Andrew. (2011). A Byteman Tutorial. \\\textit{JBoss Developer}. Retrieved from: 
-\\\texttt{https://developer.jboss.org/wiki
-/ABytemanTutorial}
+Dinn, Andrew. (2011). A Byteman Tutorial. 
+\\\textit{JBoss Developer}. Retrieved from: \\\texttt{https://developer.jboss.org/wiki/\newline ABytemanTutorial}
 
@@
 Yo Code - Extension Generator
-\\\texttt{https://code.visualstudio.com/docs
-/extensions/yocode}
+\\\texttt{https://code.visualstudio.com/docs/\newline extensions/yocode}
 
@@
 Byteman Language Extension.
-\\\texttt{https://github.com/aptmac/byteboy
-/tree/master/byteman-language-extension}
+\\\texttt{https://github.com/aptmac/byteboy/tree/\newline master/byteman-language-extension}
 
@@
 Textmate: Language Grammars
-\\\texttt{https://manual.macromates.com/en
-/language\_grammars}
+\\\texttt{https://manual.macromates.com/en/\newline language\_grammars}
 
@@
 HPROF: A Heap/CPU Profiling Tool
-\\\texttt{https://docs.oracle.com/javase/7/docs/technotes
-/samples/hprof.html}
+\\\texttt{https://docs.oracle.com/javase/7/\newline docs/technotes/samples/hprof.html}
 
@@
 javap - The Java Class File Disassembler
-\\\texttt{https://docs.oracle.com/javase/7/docs/technotes
-/tools/windows/javap.html}
+\\\texttt{https://docs.oracle.com/javase/7/\newline docs/technotes/tools/windows/javap.html}
 

### 2017-12-08 final-paper/paper.la_.tex
feat(paper): added synthesis section

@@
 
-Majority of the work required for Byteboy is analysing the results from HPROF and presenting it back to the reader in a useful manner.
+Majority of the work required for Byteboy is analyzing the results from HPROF and presenting it back to the reader in a useful manner.
 We decided to use Python to handle this task as it was the most accessable and lightweight language available.
@@
 
-This is where we discuss how the rules get mashed together.
+Byteboy currently offers four different types of rule construction: manual, semi-automatic, automatic, and fuzz test generator.
+
+In manual, Byteboy goes through the required components of Byteman rule syntax, and prompts the user for input for each of the required fields.
+The end result is a rule constructed based solely on the information provided by the user, and is reminiscent of the Yo Code generator\cite{yocode}.
+
+In semi-automatic, the process is the same as manual, with the addition of information gathered from the analysis phase.
+Each Byteman rule component (with the exception of the DO block) can be auto-filled by simply pressing the enter key, and Byteboy will supply the highest ranking choice based on the analysis.
+However, the user is able to freely enter information here as they please, and use the displayed analytics to craft their own rules based on the result of their program's execution.
+
+In automatic, Byteboy creates a set of rules to trace application behaviour.
+A set of rules are created that alert the console when methods are called, which will provide real-time status reports to the user when running their program with these injected rules.
+
+In fuzz test generator, Byteboy creates a set of rules that are intended to test the durability and resilience of the source program.
+Byteboy uses the analysis data, and figures out what the data type of each functions parameters are.
+Next, a rule is constructed that replaces the variable in the function declaration with a randomized value provided by one of our many helper functions.
+We currently have functionality to randomize the information of int, long, float, double, boolean, and String data types.
+The goal of these generated rules are to see if randomized inputs can be used to crash the source program, or cause ill effects.
 
@@
 This paper has presented Byteboy, a companion application suite for Byteman that includes a manual and semi-automatic rule generator, a fuzz test generator, and a VS Code language extension.
-Byteboy has shown that it can produce rules that may be of use to developers, but will require additional work towards refining and strengthening it's functionality.
+Byteboy has shown that it can produce rules that may be of use to developers (for tracing and fuzzing purposes), but will require additional work towards broadening and strengthening it's functionality.
 
@@
 
+\bibitem{bytemanvideo}
+Dinn, Andrew. \\\textit{Monitoring Application-Specific Behavior Using Thermostat and Byteman}
+YouTube. 2016. URL: \\\texttt{https://www.youtube.com/watch?v=teL7qnulUTM}
+
 \bibitem{yoman}
-Yeoman.
+Yeoman: The web's scaffolding tool for modern webapps.
 \\\texttt{http://yeoman.io/}
@@
 \\\texttt{https://code.visualstudio.com/docs/\newline extensions/yocode}
+
+\bibitem{byteboy}
+Byteboy: A Byteman Companion Application.
+\\\texttt{https://github.com/aptmac/byteboy}
 
@@
 \\\texttt{https://manual.macromates.com/en/\newline language\_grammars}
-
-\bibitem{bytemanvideo}
-Dinn, Andrew. \\\textit{Monitoring Application-Specific Behavior Using Thermostat and Byteman}
-YouTube. 2016. URL: \\\texttt{https://www.youtube.com/watch?v=teL7qnulUTM}
-
-\bibitem{byteboy}
-Byteboy.
-\\\texttt{https://github.com/aptmac/byteboy}
 

### 2017-12-08 final-paper/paper.la_.tex
feat(paper): added limitations section

@@
 
-Discuss the limitations of our work.
+Currently, Byteboy has several limitations that confines it's use cases.
+For starters, Byteboy accepts a Java file with the extension {\tt .java} or {\tt .class} as input, however, many larger applications are not simply launched through the command-line using the {\tt java} command.
+Many popular Java applications may be packaged in {\tt .jar} format as an executable, or rely on larger build systems such as Maven and Gradle which makes the situation trickier.
+
+The rules generated by Byteboy currently provide tracing and fuzz test capabilities, and this is reflective of our current product knowledge of Byteman and not the capabilities of Byteman as a tool.
+There are many more intricate and complicated types of rules that could be created, and using the data from our analysis it may allow for these rules to be created.
+However, it's difficult to create a code generator for a language when we aren't masters of the language ourselves, so this limited functionality should be seen as a proof of concept, and open the doors to future improvements in this application.
+
+Lastly, the fuzz test generator only handles primitive data types at the moment, and doesn't work with arrays.
+The ability to fuzz arrays would be an interesting addition of functionality for the future, and allowing for the fuzzing of Java-specific data types (or even custom data types) would be an interesting topic of research as well.
 
@@
 Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
-\\\texttt{http://downloads.jboss.org/byteman/\newline3.0.10/ProgrammersGuide.html}
+\\\texttt{http://downloads.jboss.org/byteman/\newline 3.0.10/ProgrammersGuide.html}
 

### 2017-12-08 final-paper/paper.la_.tex
chore(paper): general clean-up and grammar checking

@@
 
-This paper presents Byteboy, a companion application suite for Byteman which includes a semi-automatic rule builder, a VS Code language extension, and a basic fuzz test generator for the Byteman scripting language.
+This paper presents Byteboy, a companion application suite for Byteman which includes a semi-automatic and automatic rule builder, a VS Code language extension, and a basic fuzz test generator for the Byteman scripting language.
 
@@
 Modern compilers and testing frameworks will often help developers minimize the number of bugs that make it into production environments, but there is no guarantee that the end result will be completely error free.
-For example, a Java program with poor exception handling coverage may pass a syntax check, but will crash if an unexpected exception type is thrown in response to an input.
+For example, a Java program with poor exception handling coverage may pass a syntax check, but will crash if an unexpected exception type is thrown in response to an unexpected input.
 As a result, there is a need for tools that can diagnose and repair software bugs in runtime environments, and can interact with the program code in order to either create a temporary fix, or reveal the root cause of the error such that a proper fix can be developed.
@@
 In this paper, we propose Byteboy\cite{byteboy}, a companion application for Byteman.
-Byteboy provides functionality for manual and semi-automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension.
+Byteboy provides functionality for manual, semi-automatic, and automatic rule generation, fuzz test generation, and a Visual Studio Code Byteman rule language extension.
 Byteboy was designed to improve the Byteman user experience from the point of rule inception, through to actually implementing and shipping the proposed bug-fixing rule file.
@@
 
-Here, we wish to present Byteboy - a companion application for Byteman.
+Here, we introduce Byteboy - a companion application for Byteman.
 Byteboy was designed to enhance the Byteman user experience by aiding the development of rules starting from the point of inception, through to the result of creating in a production-quality script.
@@
 The semi-automatic rule generation actually performs an execution of the target program, and collects and aggregates information about the application performance and code structure to generate a set of plausible rules.
+The automatic rule generator creates a set of rules that can be used to trace the activity of a program in execution.
 
@@
 The language extension is not yet currently available through the Extensions Marketplace, but future work efforts will be put forward towards a public release.
-Currently, the only method of installation would be to grab the {\tt byteman-language-extension} folder from the Byteboy repository, and copying it into the extensions folder located in the VS Code user settings folder.
+Currently, the only method of installation would be to grab the {\tt byteman-language-extension} folder from the Byteboy repository\cite{byteboy}, and copying it into the extensions folder located in the VS Code user settings folder.
 On Linux, this can be accomplished using the following command:
@@
 Currently, Byteboy has several limitations that confines it's use cases.
-For starters, Byteboy accepts a Java file with the extension {\tt .java} or {\tt .class} as input, however, many larger applications are not simply launched through the command-line using the {\tt java} command.
+For starters, Byteboy accepts a Java program with the extension {\tt .java} or {\tt .class} as input, however, many larger applications are not simply launched through the command-line using the {\tt java} command.
 Many popular Java applications may be packaged in {\tt .jar} format as an executable, or rely on larger build systems such as Maven and Gradle which makes the situation trickier.

### 2017-12-08 final-paper/paper.la_.tex
Added related work information

@@
 
-This is where related work goes. \\
+\subsection{ByteBuddy}
+ByteBuddy is a popular code generation and manipulation library for creating and modifying Java classes during the runtime of a Java application\cite{bytebuddy}.
+The bytebuddy library allows a user can inject classes into a running JVM dynamically.
+Since it is a Java library, it is easier and more intuitive than Byteman rules.
+However, we do believe that the simplicity of Byteman rules are perferred compared to learning a new library.
+
+\subsection{AspectJ}
+Aspect-oriented programming (AOP) is a way of modularizing crosscutting concerns much like object-oriented programming is a way of modularizing common concerns\cite{aspectj}.
+When we have to use methods (ex.
+logging) that are used throughout different methods that span different classes, it can lead to code tangling or scattering.
+AspectJ is an extension to java that allows for the AOP paradigm to work alongside with object-oriented programming.
 
@@
 
+\bibitem{bytebuddy}
+ByteBuddy
+\\\texttt{http://bytebuddy.net/}
+
+\bibitem{aspectj}
+Introduction to aspectj
+\\\texttt{https://www.eclipse.org/aspectj/doc/released/progguide/starting-aspectj.html}
+
 \end{thebibliography}

### 2017-12-08 final-paper/paper.la_.tex
fix(paper): fixed formatting in references so outputted pdf citations work, + small grammatical fix

@@
 ByteBuddy is a popular code generation and manipulation library for creating and modifying Java classes during the runtime of a Java application\cite{bytebuddy}.
-The bytebuddy library allows a user can inject classes into a running JVM dynamically.
+The bytebuddy library allows a user to inject classes into a running JVM dynamically.
 Since it is a Java library, it is easier and more intuitive than Byteman rules.
@@
 Introduction to aspectj
-\\\texttt{https://www.eclipse.org/aspectj/doc/released/progguide/starting-aspectj.html}
+\\\texttt{https://www.eclipse.org/aspectj/doc/\newline released/progguide/starting-aspectj.html}
 

### 2017-12-08 final-paper/paper.la_.tex
Added finishing paragraph to related work

@@
 
+Similar to ByteBuddy, there doesn't seem to be any work on recommendations of what classes to modify.
+Both tools require a decent amount of knowledge of the target source code.
+ByteBoy could eventually, using its HPROF and {\tt javap} anaylsis, support ByteBuddy and AspectJ synthesis as well.
+However, code synthesis for both of these tools would prove to be a different challenge on its own.
+
 \section{CONCLUSION \& FUTURE WORK}

### 2017-12-08 final-paper/paper.la_.tex
added an additional sentence relating back to related work in conclusion/futurework
chore(paper): cleaned up a couple of typos

@@
 Both tools require a decent amount of knowledge of the target source code.
-ByteBoy could eventually, using its HPROF and {\tt javap} anaylsis, support ByteBuddy and AspectJ synthesis as well.
+Byteboy could eventually, using its HPROF and {\tt javap} analysis, support ByteBuddy and AspectJ synthesis as well.
 However, code synthesis for both of these tools would prove to be a different challenge on its own.
@@
 Additionally, more work will be done to improve the grammar file of the language extension, and it will hopefully be available for download via the Visual Studio Marketplace in the near future.
+Support for other existing Java tools, such as AspectJ and ByteBuddy, could be useful as developers would not need to learn an additional language (Byteman).
 

### 2017-12-08 final-paper/paper.la_.tex
chore(paper): added some final edits and updates to the latex file, attached pdf version

@@
 
-This paper presents Byteboy, a companion application suite for Byteman which includes a semi-automatic and automatic rule builder, a VS Code language extension, and a basic fuzz test generator for the Byteman scripting language.
+This paper presents Byteboy, a companion application suite for Byteman which includes a manual, semi-automatic and automatic rule builder, a VS Code language extension, and a basic fuzz test generator for the Byteman scripting language.
 
@@
 For example, a Java program with poor exception handling coverage may pass a syntax check, but will crash if an unexpected exception type is thrown in response to an unexpected input.
-As a result, there is a need for tools that can diagnose and repair software bugs in runtime environments, and can interact with the program code in order to either create a temporary fix, or reveal the root cause of the error such that a proper fix can be developed.
+As a result, there is a need for tools that can diagnose and repair software bugs in runtime environments, and can interact with the program code in order to either create a temporary fix or reveal the root cause of the error such that a proper fix can be developed.
 
@@
 Byteman modifies the bytecode of an application at runtime, and can inject into any Java methods (including the JDK runtime and libraries), and can even interact with private methods\cite{bytemanwebsite}.
-Unlike many other bytecode transformers, Byteman operates at the level of Java (not bytecode), so you provide Byteman with rules with specify the Java code you want to be executed, and Byteman works out how to rewrite the bytecode such that it behaves as if it were native to the source code\cite{bytemanwebsite}.
+Unlike many other bytecode transformers, Byteman operates at the level of Java (not bytecode), so you provide Byteman with rules which specify the Java code you want to be executed, and Byteman works out how to rewrite the bytecode such that it behaves as if it were native to the source code\cite{bytemanwebsite}.
 
@@
 \noindent
-The syntax of a Byteman rule is as follows:
+The general syntax of a Byteman rule is as follows:
 
@@
 
-{\tt CLASS} specifies the class the rule wants to target.
+{\tt CLASS} specifies the Java class the rule wants to target.
 
@@
 
-If {\tt BYTEMAN\_HOME} is an environment variable that points to the current installed or downloaded version of Byteman, a script ({\tt rule.btm} in this case) can be loaded along side running the Java program {\tt HelloWorld} with the following command:
+Suppose {\tt BYTEMAN\_HOME} is an environment variable that points to the current installed or downloaded version of Byteman, a script ({\tt rule.btm} in this case) can be loaded along side running the Java program {\tt HelloWorld} with the following command:
 
@@
 Here, we introduce Byteboy - a companion application for Byteman.
-Byteboy was designed to enhance the Byteman user experience by aiding the development of rules starting from the point of inception, through to the result of creating in a production-quality script.
+Byteboy was designed to enhance the Byteman user experience by aiding the development of rules starting from the point of rule inception, through to the result of creating in a production-quality script.
 
-The primary functionality of Byteboy is it's rule generator, which can be used in a manual or semi-automatic capacity.
+The primary functionality of Byteboy is it's rule generator, which can be used in a manual, semi-automatic, and automatic mode.
 The manual rule generation using Byteboy is reminiscent of the Yeoman Generator\cite{yoman}, in which the program will guide new and first-time users through the process of writing rules.
@@
 
-Another feature of Byteboy is it's fuzz test generator, in which it performs the same analysis of the semi-automatic rule generation, but instead of suggesting rules that could be used to trace or debug the code, it generates rules with the aim of producing unexpected behaviour in the source program.
+Another feature of Byteboy is it's fuzz test generator, in which it performs similarilty to the automatic functionality, but instead of suggesting rules that could be used to trace  the code, it generates rules with the aim of producing unexpected behaviour in the source program.
 
@@
 In the case of {\tt InfLoop.java}, the generated test actually caused the previously infinite loop to exit, ceasing execution of the program.
-While we are pleased with the initial results of the fuzz test generator functionality, there are many cases that cannot be properly handled, and we will explain these situations in the Limitations part of this paper.
+While we are pleased with the initial results of the fuzz test generator functionality, there are many cases that cannot be properly support, and we will explain these situations in the Limitations part of this paper.
 
@@
 Byteman is a powerful tool for tracing and debugging Java programs by injecting code into running application methods, but currently lacks the luxuries of modern programming languages.
-This paper has presented Byteboy, a companion application suite for Byteman that includes a manual and semi-automatic rule generator, a fuzz test generator, and a VS Code language extension.
+This paper has presented Byteboy, a companion application suite for Byteman that includes a manual, semi-automatic, and automatic rule generator, a fuzz test generator, and a VS Code language extension.
 Byteboy has shown that it can produce rules that may be of use to developers (for tracing and fuzzing purposes), but will require additional work towards broadening and strengthening it's functionality.
